Classification of short product Reviews using Semi-Supervised Learning

### 2012-09-02 docs/paper.tex
Added experiments details

\section{Datasets}
The Datasets of this experiments were provided by Meridean.\\
Meridean\footnote{\url{http://http://merideangroup.com/}} is a Colombian company which extracts tweets
mentioning latinamerican companies or products.\\
\\
The datasets are separated by product.\\
There are 3 datasets in this experiment:
\begin{itemize}
	\item Clothing-Brand dataset
	\item Mobile-Phone dataset
	\item hygienic-product dataset
\end{itemize}

@@

@@

\subsection{Algorithm}
Let $Y_{ij}$ be the soft probability of labeling instance $i$ with label $j$.\\
\\
Given our semi-supervised task, then $Y$ can be divided into:\\
\\
$Y_{U}$:the soft labels for the unlabelled data\\
$Y_{L}$:the soft labels for the labelled data\\
\\
This means that $Y_{L}$ is given at the beginning of the problem
and the target is to find good values for $Y_{U}$.\\
\\
\textbf{Step 1 - Init}: In this step, the Labels for $Y_{L}$ are clamped, and the labels for $Y_{U}$ are randomly initialized.\\
The proof that the initialization values of $Y_{U}$ are not transcendental can be found at ~\cite{Zhu:2005:SLG:1104523}.\\
\\
\textbf{Step 2 - Propagation}: In this step, the Labels of neighbouring nodes are pushed.\\
Let $t$ be the current iteration, then $Y^{t+1}$ is defined as:
\begin{align}
Y^{t+1} = T Y^{t}
\end{align}
\\
\textbf{Step 3 - Clamp Labelled Data}: In this step, the Labels for $Y_{L}$ are clamped.\\
\\
\textbf{Step 4 - Repeat}: Repeat from step 2 until convergence.\\
\\
\textbf{Step 5 - Labeling Approach}: Once there is convergence, a label has to be chosen for each node in the graph, there is more than one approach.\\
The simplest approach would be to pick the label with the highest probability. \\
In ~\cite{Zhu:2005:SLG:1104523} there is an empirical analysis on more sophisticated approaches, there it is shown how this criteria can affect the performance, nevertheless for this experiment the simple approach was used.\\
\\
To summarize, in the experiment we convert our data into a complete graph,
each node is the feature vector of a comment, and the weight of each arc
corresponds to the similarity of the comments being incident to the arc.\\
This Graph is  fed to the Label Propagation Algorithm.

\section{Structure Learning}
A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
This paper proposes a way to learn multiple classification tasks.In this approach the original Classification Task(Target Problem) is extended by creating a set of auxiliary classification tasks.\\
The Auxiliary Classification tasks are used to improve performance on the target task,
the underlying assumption is that by solving the auxiliary problems one should be able to find good predictive structures.\\
The Auxiliary Tasks are trained on the unlabeled data,in consequence one constraint to the creation of auxiliary tasks is that they should be able to automatically generate training data from the target's problem unlabelled data.In ~\cite{Ando:2005:HSL:1219840.1219841} it is argued that having a high number of auxiliary tasks is beneficial for the performance.\\
\\
In this paper's experiment, the target task corresponds to find the label of each comment.\\
The auxiliary problems are defined as:\\
Learn a linear predictor using the Unlabelled data for the $K$ most common words in the unlabeled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
\\
For learning this tasks, first the Words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained from the comments.\\
\\
By solving the auxiliary tasks, the feauture vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
This might shown useful in the setup of the experiment, since we are extending the feauture representations from knowledge of unlabelled data.\\
\\
Finally a linear classifier is learnt using the training data for the target problem.

@@

\section{Experiment}
For the experiments, the three datasets mentioned above were used as training and test data.\\
The experiments corresponds to the following:
\begin{itemize}
	\item Single task Supervised Learning using SVM (SVM)
	\item Single task Semi-supervised Learning using Label Propagation (LP)
	\item Single task Semi-supervised Learning using Structural Learning(Single-SL)
	\item Multitask Semi-supervised Learning using Structural Learning(Multi-SL)
\end{itemize}

An OpenSource implementation of Label Propagation was used $Junto$\footnote{ \url{https://github.com/parthatalukdar/junto} }.\\
\\
For SL, the libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} library provided an implementation for training SVM.

@@

\section{Future Work}

>>>>

\section{Datasets}
The Datasets of this experiments were provided by Meridean.\\
Meridean\footnote{\url{http://http://merideangroup.com/}} is a Colombian company which extracts tweets
mentioning latinamerican companies or products.\\
\\
The datasets are separated by product.\\
There are 3 datasets in this experiment:
\begin{itemize}
	\item Sportwear dataset
	\item Mobile-Phone dataset
	\item hygienic-product dataset
\end{itemize}

@@

Each dataset contains approximately 5000 tuples.

@@

\subsection{Algorithm}
Let $Y_{ij}$ be the soft probability of labeling instance $i$ with label $j$.\\
\\
Given our semi-supervised task, then $Y$ can be divided into:\\
\\
$Y_{U}$:the soft labels for the unlabelled data\\
$Y_{L}$:the soft labels for the labelled data\\
\\
This means that $Y_{L}$ is given at the beginning of the problem
and the target is to find good values for $Y_{U}$.\\
\\
\textbf{Step 1 - Init}: In this step, the Labels for $Y_{L}$ are clamped, and the labels for $Y_{U}$ are randomly initialized.\\
The proof that the initialization values of $Y_{U}$ are not transcendental can be found at ~\cite{Zhu:2005:SLG:1104523}.\\
\\
\textbf{Step 2 - Propagation}: In this step, the Labels of neighbouring nodes are pushed.\\
Let $t$ be the current iteration, then $Y^{t+1}$ is defined as:
\begin{align}
Y^{t+1} = T Y^{t}
\end{align}
\\
\textbf{Step 3 - Clamp Labelled Data}: In this step, the Labels for $Y_{L}$ are clamped.\\
\\
\textbf{Step 4 - Repeat}: Repeat from step 2 until convergence.\\
\\
\textbf{Step 5 - Labeling Approach}: Once there is convergence, a label has to be chosen for each node in the graph, there is more than one approach.\\
The simplest approach would be to pick the label with the highest probability. \\
In ~\cite{Zhu:2005:SLG:1104523} there is an empirical analysis on more sophisticated approaches, there it is shown how this criteria can affect the performance, nevertheless for this experiment the simple approach was used.\\
\\
More sophisticated versions of this approach have been presented and assessed, in ~\cite{Talukdar:2010:EGS:1858681.1858830} Talukdar and Pereira showed an empirical comparison among different variations of the LP algorithm, a modified absortion algorithm is presented where seed labels are not clamped,and it is shown to have better performance in the given tasks.
Nevertheless within this paper we call LP to the algorithm proposed by Zhu ~\cite{Zhu:2005:SLG:1104523}.\\
\\
To summarize, in the experiment we convert our data into a complete graph,
each node is the feature vector of a comment, and the weight of each arc
corresponds to the similarity of the comments being incident to the arc.\\
This Graph is  fed to the Label Propagation Algorithm proposed by Zhu.\\

\section{Structure Learning}
A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
This paper proposes a way to learn multiple classification tasks.In this approach the original Classification Task(Target Problem) is extended by creating a set of auxiliary classification tasks.\\
The Auxiliary Classification tasks are used to improve performance on the target task,
the underlying assumption is that by solving the auxiliary problems one should be able to find good predictive structures.\\
The Auxiliary Tasks are trained on the unlabeled data,in consequence one constraint to the creation of auxiliary tasks is that they should be able to automatically generate training data from the target's problem unlabelled data.In ~\cite{Ando:2005:HSL:1219840.1219841} it is argued that having a high number of auxiliary tasks is beneficial for the performance.\\
\\
In this paper's experiment, the target task corresponds to find the label of each comment.\\
The auxiliary problems are defined as:\\
Learn a linear predictor using the Unlabelled data for the $K$ most common words in the unlabeled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
\\
For learning this tasks, first the Words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained from the comments.\\
\\
By solving the auxiliary tasks, the feauture vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
This might shown useful in the setup of the experiment, since we are extending the feauture representations from knowledge of unlabelled data.\\
\\
Finally a linear classifier is learnt using the training data for the target problem.\\
With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.

@@

\section{Experiment}
For the experiments, the three datasets mentioned above were used as training and test data.\\
The experiments corresponds to the following:
\begin{itemize}
	\item Single task Supervised Learning using SVM ($SVM$)
	\item Single task Semi-supervised Learning using Label Propagation ($LP$)
	\item Single task Semi-supervised Learning using The naive Structural Learning($SL$)

\end{itemize}

Each of the experiments were ran with different amounts of training data, specifically 10\%, 30\%, 60\% and 90\%\\
\\
For the Label Propagation  $Junto$ \footnote{ \url{https://github.com/parthatalukdar/junto} } ~\cite{Talukdar:2010:EGS:1858681.1858830} was used. $Junto$ is an open source implementation of the Label Propagation algorithm proposed by Zhu.\\
\\
For $SL$ and $SVM$ the libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} library provided an implementation for training SVM.\\
For all the linear classifiers trained in the experiments a  polynomial Kernel was picked and the value of $gamma$ was 1.2, the reason behind this choice is motivated by the empirical results obtained by ~\cite{Joachims:1998:TCS:645326.649721} in a similar task.

@@

\section{Future Work}
%other LP variations ( MAD for noisy ..)
%multitask
%more feautures for running
%extending the comments with extra knowledge
%better preprocesing
